Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-15 cover_letter.tex
Addressed question on TUM or LMU?
Addressed question on robots architectures + some typography fix

\subsection{``VI. the authors are advised to present an initial overview of the
robot hardware and the common software architecture used in the systems''}

@@

>>>>

\subsection{``Present an initial overview of the
robot hardware and the common software architecture used in the systems''}

Paragraph added in the section 6 introduction.

@@

The study was conducted with TUM in Munich. This has been corrected in 
the paper as well.

### 2011-07-15 paper_knowledge.tex
Addressed question on TUM or LMU?
Addressed question on robots architectures + some typography fix

	\vspace{0.5em}
	\emph{Generated partial statements}\\
	\hline
	\hspace{0.3cm}\stmt{?obj type Banana} \\
    	\hspace{0.3cm}\stmt{?obj hasColor yellow} \\
    	\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = banana\_01}\\

@@

	\begin{tabular}{p{7cm}}
	\emph{Generated partial statements}\\
	\hline
    	\hspace{0.3cm}\stmt{?obj type Banana} \\
	\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = banana\_01}\\

@@

@@

\begin{center}
\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = [videoTape1, videoTape2]}
\end{center}

@@

\begin{center}
{\tt ?obj = [videoTape1]}
\end{center}

@@

\begin{center}
\begin{tabular}{l}
\stmt{?obj type Box}\\
\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = [cardBoardBox, toolbox]}
\end{tabular}
\end{center}

However both are visible and the cognitive ambiguity resolution cannot be
applied. The only option is to ask Jerry which box he is referring to: ``Which
box, the toolbox or the cardboard box?'' Jerry could now simply answer the
question. Instead, he decides to point at it while indicating: ``This box''
(Figure~\ref{fig|pointing}b). The robot's perception identifies the {\tt
cardBoardBox} as being pointed at and looked at by the human and updates the
ontology with this new information using a rule available in the commonsense
ontology ({\tt pointsAt(?ag, ?obj) $\land$ looksAt(?ag, ?obj) $\to$
focusesOn(?ag, ?obj)}) The \textsc{Dialogs} module is then able to merge both
sources of information, verbal (``this'') and gestural to distinguish the box
Jerry refers to.

\begin{center}
\begin{tabular}{l}
\stmt{Jerry pointsAt carboardBox}\\
\stmt{Jerry looksAt carboardBox}\\
$\to$ \stmt{Jerry focusesAt carboardBox}\\
\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = [cardBoardBox]}
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{l}
\stmt{?obj isIn cardBoardBox}\\
\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = videoTape2}\\
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{l}
\stmt{?obj type VideoTape}\\
\stmt{?obj differentFrom videoTape2}\\
\hspace{0.7cm}$\Rightarrow$ {\tt ?obj = [videoTape1]}
\end{tabular}
\end{center}

>>>>

	\vspace{0.5em}
	\emph{Generated partial statements}\\
	\hline
	\hspace{0.3cm}\stmt{?obj type Banana} \\
    	\hspace{0.3cm}\stmt{?obj hasColor yellow} \\
    	\hspace{0.7cm}$\Rightarrow$ \concept{?obj = banana\_01}\\

@@

	\begin{tabular}{p{7cm}}
	\emph{Generated partial statements}\\
	\hline
    	\hspace{0.3cm}\stmt{?obj type Banana} \\
	\hspace{0.7cm}$\Rightarrow$ \concept{?obj = banana\_01}\\

@@

Experiments have been conducted on two different platforms: the
\emph{Rosie} manipulator from the Technical Universtiy of Munich, a dual-arm,
holonomic service robot, running the ROS\footnote{\emph{Robotic Operating
System}, \url{http://www.ros.org}} middleware, and the \emph{Jido} robot from
LAAS-CNRS, a similar, single-arm, service robot, running the LAAS's {\sc
Genom/pocolibs} stack.

@@

\begin{center}
\hspace{0.7cm}$\Rightarrow$ \concept{?obj = [videoTape1, videoTape2]}
\end{center}

@@

\begin{center}
\concept{?obj = [videoTape1]}
\end{center}

@@

\begin{center}
\begin{tabular}{l}
\stmt{?obj type Box}\\
\hspace{0.7cm}$\Rightarrow$ \concept{?obj = [cardBoardBox, toolbox]}
\end{tabular}
\end{center}

However both are visible and the cognitive ambiguity resolution cannot be
applied. The only option is to ask Jerry which box he is referring to: ``Which
box, the toolbox or the cardboard box?'' Jerry could now simply answer the
question. Instead, he decides to point at it while indicating: ``This box''
(Figure~\ref{fig|pointing}b). The robot's perception identifies the
\concept{cardBoardBox} as being pointed at and looked at by the human and
updates the ontology with this new information using a rule available in the
commonsense ontology ({\tt pointsAt(?agt, ?obj) $\land$ looksAt(?agt, ?obj)
$\to$ focusesOn(?agt, ?obj)}) The \textsc{Dialogs} module is then able to merge
both sources of information, verbal (``this'') and gestural to distinguish the
box Jerry refers to.

\begin{center}
\begin{tabular}{l}
\stmt{Jerry pointsAt carboardBox}\\
\stmt{Jerry looksAt carboardBox}\\
$\to$ \stmt{Jerry focusesAt carboardBox}\\
\hspace{0.7cm}$\Rightarrow$ \concept{?obj = [cardBoardBox]}
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{l}
\stmt{?obj isIn cardBoardBox}\\
\hspace{0.7cm}$\Rightarrow$ \concept{?obj = videoTape2}\\
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{l}
\stmt{?obj type VideoTape}\\
\stmt{?obj differentFrom videoTape2}\\
\hspace{0.7cm}$\Rightarrow$ \concept{?obj = [videoTape1]}
\end{tabular}
\end{center}
